Why robot programming is hard

### 2014-08-28 paper.tex
More work

% Hai Nguyen's ROCON
% Maya's Robot PBD
% Strips style robot planning

@@

In addition to the low level concurrency needed to control multiple robot parts, there is also a need to specify concurrent robot behavior at a higher level~\cite{cakmak-hri13}. For example, a user may want to give the robot background tasks (such as cleaning or plugging oneself in when the battery is low) which might be scheduled in concert with foreground tasks (such as fetching a drink).

@@

End user programming systems have tried various techniques to deal with the problem of concurrency. Some systems visualize the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand\footnote{https://www.apple.com/mac/garageband/} or Autodesk's 3D Studio Max\footnote{http://www.autodesk.com/products/3ds-max/overview}. A second paradigm, taken by visual programming languages such as Scratch~\cite{scratch}, makes the notion of time a global constant and runs all blocks of user code simultaneously in the virtual environment. More research is needed to discover what paradigm works best for controlling robot parts concurrently.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models~\cite{darwiche-cacm10} and craft fault-tolerant code~\cite{wright-cacm09} with frequent error checking. Nguyen's ROS Commander (ROSCo) system is an end-user programming system aimed to enable home users to define new behaviors for PR2 robots by visually crafting finite state machines~\cite{nguyen-icra13}. ROSCo XXX TODO

which seems like too much to ask of casual programmers who just want to teach their robot to do something useful in the home.

@@

As another example, robots that are capable of automated navigation may fail to observe human norms when navigating through human spaces. The custom of staying to the right when passing in a hallway, for example, can cause confusion if a robot charges down the middle of the hall and does not yield to oncoming passerby.

Endowing computers with common sense is still an active research area~\cite{mueller-cacm09}. Techniques for making use of common sense reasoning have not yet made it into the vocabulary of professional programmers. Yet these concepts will be taken for granted by end users of robots, who will expect their robots to obey common social norms as they perform their tasks.

>>>>

% Maya's Robot PBD
% Strips style robot planning

@@

In addition to the low level concurrency needed to control multiple robot parts, there is also a need to specify concurrent robot behavior at a higher level~\cite{cakmak-hri13}, or across multiple robots. For example, a user may want to give the robot background tasks (such as cleaning or plugging oneself in when the battery is low) which might be scheduled in concert with foreground tasks (such as fetching a drink), or might want to command two robots to work together to perform a task~\cite{liu-chi11}.

@@

Other end user programming systems have tried various techniques to deal with the problem of concurrency. Some systems visualize the different components on a timeline. This approach is popular with media creation tools such as Apple's GarageBand\footnote{https://www.apple.com/mac/garageband/} or Autodesk's 3D Studio Max\footnote{http://www.autodesk.com/products/3ds-max/overview}. A second paradigm, taken by visual programming languages such as Scratch~\cite{scratch}, makes the notion of time a global constant and runs all blocks of user code simultaneously in the virtual environment. More research is needed to discover what paradigm works best for controlling robot parts concurrently.

@@

In order to deal with these various types of uncertainty, professional programmers learn to use probabilistic models~\cite{darwiche-cacm10} and craft fault-tolerant code~\cite{wright-cacm09} with frequent error checking. Systems such as Nguyen's ROS Commander~\cite{nguyen-icra13} enable non-roboticists to define and customize robot behaviors, handling error conditions. However, ROS Commander's programming interface, which the authors liken to a Photoshop for robotics, still seems to have a significant learning curve, especially for casual consumers who just want to teach their robot to do something useful in the home.

@@

As another example, robots that are capable of automated navigation may fail to observe human norms when navigating through human spaces~\cite{lu-iros13}. The custom of staying to the right when passing in a hallway, for example, can cause confusion if a robot charges down the middle of the hall and does not yield to oncoming passerby.

Endowing computers with common sense is still an active research area~\cite{mueller-cacm09}, as is making use of common sense knowledge in robotics~\cite{gupta-aaai04}. Yet these concepts will be taken for granted by end users of robots, who will expect their robots to obey common social norms as they perform their tasks.
